Probability Distribution Checks

### 2017-03-23 Probability_distribution_checks.Rmd
Clean up and clarify probability distribution checks

@@

AUDPS_2015$LShB_rating_t <- AUDPS_2015$LShB_rating + 1

qqp(AUDPS_2015$LShB_rating_t, "norm")

qqp(AUDPS_2015$LShB_rating_t, "lnorm")

poisson <- fitdistr(AUDPS_2015$LShB_rating_t, "Poisson")
qqp(AUDPS_2015$LShB_rating_t, "pois", poisson$estimate)

gamma <- fitdistr(AUDPS_2015$LShB_rating_t, "gamma")
qqp(AUDPS_2015$LShB_rating_t, "gamma",
    shape = gamma$estimate[[1]], 
    rate = gamma$estimate[[2]])
```

@@

AUDPS_2015$TShB_rating_t <- AUDPS_2015$TShB_rating + 1

qqp(AUDPS_2015$TShB_rating_t, "norm")

qqp(AUDPS_2015$TShB_rating_t, "lnorm")

poisson <- fitdistr(AUDPS_2015$TShB_rating_t, "Poisson")
qqp(AUDPS_2015$TShB_rating_t, "pois", poisson$estimate)

gamma <- fitdistr(AUDPS_2015$TShB_rating_t, "gamma")
qqp(AUDPS_2015$TShB_rating_t, "gamma",
    shape = gamma$estimate[[1]], 
    rate = gamma$estimate[[2]])
```

@@

AUDPS_2016$LShB_rating_t <- AUDPS_2016$LShB_rating + 1

qqp(AUDPS_2016$LShB_rating_t, "norm")

qqp(AUDPS_2016$LShB_rating_t, "lnorm")

poisson <- fitdistr(AUDPS_2016$LShB_rating_t, "Poisson")
qqp(AUDPS_2016$LShB_rating_t, "pois", poisson$estimate)

gamma <- fitdistr(AUDPS_2016$LShB_rating_t, "gamma")
qqp(AUDPS_2016$LShB_rating_t, "gamma",
    shape = gamma$estimate[[1]], 
    rate = gamma$estimate[[2]])
```

@@

AUDPS_2016$TShB_rating_t <- AUDPS_2016$TShB_rating + 1

qqp(AUDPS_2016$TShB_rating_t, "norm")

qqp(AUDPS_2016$TShB_rating_t, "lnorm")

poisson <- fitdistr(AUDPS_2016$TShB_rating_t, "Poisson")
qqp(AUDPS_2016$TShB_rating_t, "pois", poisson$estimate)

gamma <- fitdistr(AUDPS_2016$TShB_rating_t, "gamma")
qqp(AUDPS_2016$TShB_rating_t, "gamma",
    shape = gamma$estimate[[1]], 
    rate = gamma$estimate[[2]])
```

>>>>

Here we check the probability distribution that best fits these data. I'm following a method from http://ase.tufts.edu/gsc/gradresources/guidetomixedmodelsinr/mixed%20model%20guide.html. As you see in that guide, there are several distributions that can be checked, for my purposes normal or lognormal are enough so I won't check the others.

@@

qqp(AUDPS_2015$LShB_rating, "norm")

qqp(AUDPS_2015$LShB_rating, "lnorm")

```

@@

AUDPS_2015$TShB_rating <- AUDPS_2015$TShB_rating + 1

qqp(AUDPS_2015$TShB_rating, "norm")

qqp(AUDPS_2015$TShB_rating, "lnorm")

```

@@

qqp(AUDPS_2016$LShB_rating, "norm")

qqp(AUDPS_2016$LShB_rating, "lnorm")

```

@@

qqp(AUDPS_2016$TShB_rating, "norm")

qqp(AUDPS_2016$TShB_rating, "lnorm")

```

## Conclusions

To read the graphs, we want to select a distribution where most of the points fall between the dotted red lines. In this case, for the 2015 data, the leaf data fit a lognormal distribution best, for all others a normal distribution appears to be fine.
